Vp qPCR

### 2023-02-12 code/analysis_code/exploratory_monthly.qmd
Total vib
Do not need to manually add in raw data

Load Data
```{r}
copies<- read_csv(here("data", "processed_data", "clean_copies_date.csv")) #This is the clean_data.csv from copies_calculator but with date manually added in,
```

@@

#Monthly All sites
monthly<- copies %>%
  select(date,copies_mL,site,Type) %>%
  filter(Type %in% "Monthly")

@@

Total Monthly Vibrio
```{r}
tot_vib_allsites_monthly <- monthly %>% ggplot()+geom_line(
  aes(x = date,
      y = copies_mL,
      color = site))+
  facet_wrap(~site) +
  theme_bw()+
  labs(
    x = "Date",
    y = "Copies/mL",
    title = "Total Monthly Vibrio at all Sites") +
  theme(plot.title = element_text(hjust = 0.5)) + #center title
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + #Tilt x axis labels 
  theme(legend.position = "none") #Removes legend

>>>>

Load Data
```{r}
copies<- read_csv(here("data", "processed_data", "total_clean_copies.csv")) #This is the clean_data.csv from copies_calculator but with date manually added in,
```

@@

#Monthly All sites
monthly<- copies %>%
  select(date,copies_mL,site,Type) %>%
  filter(Type %in% "Monthly") #Need to add July date here somehow

@@

Total Monthly Vibrio
```{r}
tot_vib_allsites_monthly <- monthly %>%
  ggplot()+geom_line(
  aes(x = date,
      y = copies_mL,
      color = site))+
  geom_point(
    aes(x = date,
        y = copies_mL,
        color = site ))+
  facet_wrap(~site) +
  theme_bw()+
  labs(
    x = "Date",
    y = "Copies/mL",
    title = "Total Monthly Vibrio at all Sites",
    caption = "This includes 3 May events and does not include July") +
  theme(plot.title = element_text(hjust = 0.5)) + #center title
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + #Tilt x axis labels 
  theme(legend.position = "none") #Removes legend

### 2023-02-12 code/processing_code/vp_copies_calculator.qmd
Total vib
Do not need to manually add in raw data

*This dataset is Daily Vv qPCR*

@@

filter<- dilution %>%
   mutate(filter_amt = case_when(Sample == "BO_7"~"100",
                          Sample == "BO_8"~"100",
                          Sample == "BO_9"~"100",
                          Sample == "BO_9"~"100",
                          Sample == "BO_11"~"100",
                          Sample == "BO_12"~"50",
                          Sample == "BO_13"~"50",
                          Sample == "BO_14"~"50",
                          Sample == "BO_15"~"50",
                          Sample == "BO_16"~"30",
                          Sample == "BO_17"~"30",
                          Sample == "BO_18"~"30",
                          Sample == "BO_19"~"30",
                              site  == "C2"~ "100",
                              site == "RD"~"100"),
        filter_amt = as.numeric(filter_amt))

@@

Date Column
```{r}
date<- replace %>%
  mutate(day = substr(replace$Sample,4,5)) %>% #Creates new column `date` 
  mutate(date = case_when(day == "7"~"2022-07-07",
                         day ==  "8"~"2022-07-08",
                         day ==  "9"~"2022-07-09",
                         day ==  "11"~"2022-07-11",
                         day == "12"~"2022-07-12",
                         day ==  "13"~"2022-07-13",
                         day ==  "14"~"2022-07-14",
                         day ==  "15"~"2022-07-15",
                         day ==  "16"~"2022-07-16",
                         day == "17"~"2022-07-17",
                         day ==  "18"~"2022-07-18",
                         day == "19"~"2022-07-19"))

>>>>

@@

filter<- dilution %>%
   mutate(filter_amt = case_when(Sample == "BO_7"~"100",
                          Sample == "BO_7"~"100",
                          Sample == "BO_8"~"100",
                          Sample == "BO_9"~"100",
                          Sample == "BO_11"~"100",
                          Sample == "BO_12"~"50",
                          Sample == "BO_13"~"50",
                          Sample == "BO_14"~"50",
                          Sample == "BO_15"~"50",
                          Sample == "BO_16"~"30",
                          Sample == "BO_17"~"30",
                          Sample == "BO_18"~"30",
                          Sample == "BO_19"~"30",
                              site  == "C2"~ "100",
                              site == "RD"~"100"),
        filter_amt = as.numeric(filter_amt))

@@

Date Column
```{r}
date<- replace %>%
  mutate(day = substr(replace$Sample,4,5)) %>% #Creates new column `day` 
  mutate(date = case_when(day == "7"~"2022-07-07",
                         day ==  "8"~"2022-07-08",
                         day ==  "9"~"2022-07-09",
                         day ==  "11"~"2022-07-11",
                         day == "12"~"2022-07-12",
                         day ==  "13"~"2022-07-13",
                         day ==  "14"~"2022-07-14",
                         day ==  "15"~"2022-07-15",
                         day ==  "16"~"2022-07-16",
                         day == "17"~"2022-07-17",
                         day ==  "18"~"2022-07-18",
                         day == "19"~"2022-07-19"))
